---
title: "CalorieConversion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(cowplot)
library(ggplot2)
library(ggpubr)
library(dplyr)

#carb<-read.table("../ProcessedData/all_carb_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
#lip<-read.table("../ProcessedData/all_lip_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
#prot<-read.table("../ProcessedData/all_prot_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
#gly<-read.table("../ProcessedData/all_gly_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

###transformed
gly<-read.table("../ProcessedData/glycogen_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
carb<-read.table("../ProcessedData/carbs_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
lip<-read.table("../ProcessedData/lipid_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot<-read.table("../ProcessedData/prot_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
```
carb<-read.table("../ProcessedData/all_carb.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
gly<-read.table("../ProcessedData/all_gly.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot<-read.table("../ProcessedData/all_prot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
lip<-read.table("../ProcessedData/all_lip.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)


###This is in kilocalorie!!!

```{r}
carb$c_carb_cal<-carb[,2]*1.6
carb$dr_carb_cal<-carb[,3]*1.6
carb$hs_carb_cal<-carb[,4]*1.6
```

```{r}
lip$c_lip_cal<-lip[,2]*8
lip$dr_lip_cal<-lip[,3]*8
lip$hs_lip_cal<-lip[,4]*8
```


```{r}
prot$c_prot_cal<-prot[,2]*3.9
prot$dr_prot_cal<-prot[,3]*3.9
prot$hs_prot_cal<-prot[,4]*3.9
```

check glycogen
```{r}
gly$c_gly_cal<-gly[,2]*1.6
gly$dr_gly_cal<-gly[,3]*1.6
gly$hs_gly_cal<-gly[,4]*1.6
```

##KILO CALORIE conversion on transformed data
```{r}
write.table(prot, "../ProcessedData/prot_cal.txt", sep="\t")
write.table(carb, "../ProcessedData/carb_cal.txt", sep="\t")
write.table(gly, "../ProcessedData/gly_cal.txt", sep="\t")
write.table(lip, "../ProcessedData/lip_cal.txt", sep="\t")

```

Caloric content of phytoplankton (1973)
Authors TREVOR PLATT, BRIAN IRWIN used 
(Prosser  and  Brown 1961)  :  for  protein  4.19  cal  mg-l,  for  carbohydrate  4.2,  and  for  fat  9.5 

#clear and rerun to test.
```{r}
carb<-read.table("../ProcessedData/carb_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
lip<-read.table("../ProcessedData/lip_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot<-read.table("../ProcessedData/prot_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
gly<-read.table("../ProcessedData/gly_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

control<-cbind('RIL'=carb[,1],'carb_cal'=carb[,5],'lip_cal'=lip[,5],'prot_cal'=prot[,5],'gly_cal'= gly[,5])

tot_acq<-cbind(rowSums(control[,-1], na.rm=TRUE))

Control<-cbind('RIL'=control[,1],'carb_cal'=control[,2],'lip_cal'=control[,3],'prot_cal'=control[,4],'gly_cal'= control[,5], 'tot_acq'=tot_acq[,1] )


dr<-cbind('RIL'=carb[,1],'carb_cal'=carb[,6],'lip_cal'=lip[,6],'prot_cal'=prot[,6],'gly_cal'= gly[,6])
tot_acq<-cbind(rowSums(dr[,-1], na.rm=TRUE))
DietRes<-cbind('RIL'=dr[,1],'carb_cal'=dr[,2],'lip_cal'=dr[,3],'prot_cal'=dr[,4],'gly_cal'= dr[,5], 'tot_acq'=tot_acq[,1] )

hs<-cbind('RIL'=carb[,1],'carb_cal'=carb[,7],'lip_cal'=lip[,7],'prot_cal'=prot[,7],'gly_cal'= gly[,7])
tot_acq<-cbind(rowSums(hs[,-1], na.rm=TRUE))

HighSugar<-cbind('RIL'=hs[,1],'carb_cal'=hs[,2],'lip_cal'=hs[,3],'prot_cal'=hs[,4],'gly_cal'= hs[,5], 'tot_acq'=tot_acq[,1] )
```

```{r}
write.table(Control, "../ProcessedData/Control_tot_acq_transformed.txt", sep="\t")
write.table(DietRes, "../ProcessedData/DR_tot_acq_transformed.txt", sep="\t")
write.table(HighSugar, "../ProcessedData/HS_tot_acq_transformed.txt", sep="\t")
```

