---
title: "mapping_calories_protiencorrection_pca"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(cowplot)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(plyr)
library(multcomp)
library(forcats)
setwd("C:/Users/Anna/Dropbox/AMP_EGK/Projects/Ch1_RILs/Scripts")
```


```{r cars}
carb<-read.table("../ProcessedData/carb_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
lip<-read.table("../ProcessedData/lip_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot<-read.table("../ProcessedData/prot_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
gly<-read.table("../ProcessedData/gly_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
#these datasets have macromolecule split by diet, issues in both calories and grams (mg?)
#do I need a total acquisition column
```

can use  "map_cal.txt" here 

#protien correction. 
Only run if necessary. Protein correction not used in following calculations.

carb$c_carb_p_crt<-(carb$c_carb/prot$c_prot)
carb$dr_carb_p_crt<-(carb$dr_carb/prot$dr_prot)
carb$hs_carb_p_crt<-(carb$hs_carb/prot$hs_prot)

gly$c_gly_p_crt<-(gly$c_gly/prot$c_prot)
gly$dr_gly_p_crt<-(gly$dr_gly/prot$dr_prot)
gly$hs_gly_p_crt<-(gly$hs_gly/prot$hs_prot)

lip$c_lip_p_crt<-(lip$c_lip/prot$c_prot)
lip$dr_lip_p_crt<-(lip$dr_lip/prot$dr_prot)
lip$hs_lip_p_crt<-(lip$hs_lip/prot$hs_prot)

write.table(prot, "../ProcessedData/prot_map_cal.txt", sep="\t")
write.table(carb, "../ProcessedData/carb_map_cal.txt", sep="\t")
write.table(gly, "../ProcessedData/gly_map_cal.txt", sep="\t")
write.table(lip, "../ProcessedData/lip_map_cal.txt", sep="\t")

#############
control_tot_acq<- read.table("../ProcessedData/Control_tot_acq.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
dr_tot_acq<- read.table("../ProcessedData/DR_tot_acq.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
hs_tot_acq<- read.table("../ProcessedData/HS_tot_acq.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

hs_tot_acq[which(hs_tot_acq$RIL %in% carblist$RIL),]
ctrl_test<-control_tot_acq[complete.cases(control_tot_acq), ] #columns w NA removed. 


#PCA's
```{r}
all_molec<-read.table("../ProcessedData/all_flies_proccessed_checked.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

all_molec$RIL<-gsub("[^[:digit:]]", "", all_molec$Line)#Make RIL column
all_molec$Treat<-gsub("[[:digit:]]","",all_molec$Line)#Make Treatment column


C_diet<-subset(all_molec, Treat=="C")
DR_diet<-subset(all_molec, Treat=="DR")
HS_diet<-subset(all_molec, Treat=="HS")
C_diet<-C_diet[complete.cases(C_diet), ] #columns w NA removed. 
DR_diet<-DR_diet[complete.cases(DR_diet), ] #columns w NA removed. 
HS_diet<-HS_diet[complete.cases(HS_diet), ] #columns w NA removed. 
length(unique(c(C_diet$RIL, DR_diet$RIL, HS_diet$RIL)))

control_pca <- prcomp(~ c_perfly + lperfly +p_perfly+ g_perfly, data = C_diet, center = TRUE, scale. = TRUE)
summary(control_pca)
print(control_pca)



PCB_control<-data.frame(control_pca$x,RIL=C_diet$RIL)

dr_pca <- prcomp(~ c_perfly + lperfly +p_perfly+ g_perfly, data = DR_diet, center = TRUE, scale. = TRUE)
summary(dr_pca)
print(dr_pca)
PCB_dr<-data.frame(dr_pca$x,RIL=DR_diet$RIL)

hs_pca <- prcomp(~ c_perfly + lperfly +p_perfly+ g_perfly, data = HS_diet, center = TRUE, scale. = TRUE)
summary(hs_pca)
print(hs_pca)
PCB_hs<-data.frame(hs_pca$x,RIL=HS_diet$RIL)

#rename columns
PCB_dr<-rename(PCB_dr, c("PC1"="dr_PC1", "PC2"="dr_PC2","PC3"="dr_PC3","PC4"="dr_PC4"))
PCB_control<-rename(PCB_control, c("PC1"="ctl_PC1", "PC2"="ctl_PC2","PC3"="ctl_PC3","PC4"="ctl_PC4"))
PCB_hs<-rename(PCB_hs, c("PC1"="hs_PC1", "PC2"="hs_PC2","PC3"="hs_PC3","PC4"="hs_PC4"))


#merge
ctl_dr<-join(PCB_control, PCB_dr, by="RIL", type="full")
all_tx<-join(ctl_dr, PCB_hs, by="RIL", type="full")
```

PC <- data.frame(pc1 = total_acq_PCA$x[, 1],
                 pc2 = total_acq_PCA$x[, 2])

pc_plot <- ggplot(PC, aes(pc1, pc2)) +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_hline(yintercept = 0, color = "red", size = 1.5) +
  geom_point() +
  coord_fixed()
print(pc_plot)

```{r}
#write dataframe
write.table(all_tx, "../ProcessedData/dat_for_pcamap.txt", sep="\t")

```

#read above --> 
carb<-read.table("../ProcessedData/carb_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
lip<-read.table("../ProcessedData/lip_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot<-read.table("../ProcessedData/prot_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
gly<-read.table("../ProcessedData/gly_cal.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)


###ANOVAs
```{r}
carb<-read.table("../ProcessedData/all_carb_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
lip<-read.table("../ProcessedData/all_lip_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot<-read.table("../ProcessedData/all_prot_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
gly<-read.table("../ProcessedData/all_gly_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
```

#start here
```{r}
dat<-read.table("../ProcessedData/all_carb_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

carbalt<-data.frame('value'=c(dat[,'dr_carb'],dat[,'c_carb'],dat[,'hs_carb']),'treatment'=rep(c('dr','c', 'hs'),each=nrow(dat)), 'RIL'=rep(c(dat[,'RIL'])))

hist(carbalt$value)
carbalt$carb_T<-(carbalt$value^1/2) 

carbalt<- carbalt %>% mutate(treatment=fct_inorder(carbalt$treatment, ordered=NA))

p1a<-ggplot(data=carbalt, aes(x = treatment, y=value, color=as.factor(RIL))) +
  geom_point()+
   geom_line(aes(group = paste(as.factor(RIL)), alpha = 0.2))+
  theme(legend.position="none")+
  ylab("amount (mg/fly)")+
  stat_summary(fun.y = mean, geom = "point", size = 3, color = "black")

p1a
ggsave(p1a, file='carb_amt.pdf',width=8, height=4)


carblm<-lm(value~ treatment, data=carbalt)
summary(carblm)
anova(carblm)

#post hoc testing:
tukeyc <- glht(carblm, linfct = mcp(treatment = "Tukey"))
summary(tukeyc)
plot(tukeyc)

```
#post_hoc <- glht(carblm,mcp(Treatment = c("hs - c == 0", "hs - dr == 0")))
#summary(post_hoc)

```{r}
dat<-read.table("../ProcessedData/all_lip_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

lipalt<-data.frame('value'=c(dat[,'dr_lip'],dat[,'c_lip'],dat[,'hs_lip']),'treatment'=rep(c('dr','c', 'hs'),each=nrow(dat)), 'RIL'=rep(c(dat[,'RIL'])))

lipalt<- lipalt%>% mutate(treatment=fct_inorder(lipalt$treatment, ordered=NA))


p2a<-ggplot(data=lipalt, aes(x = treatment, y=value, color=as.factor(RIL))) +
  geom_point()+
  geom_line(aes(group = paste(as.factor(RIL)), alpha = 0.2))+
  theme(legend.position="none")+
  ylab("amount (mg/fly)")+
  stat_summary(fun.y = mean, geom = "point", size = 3, color = "black")

p2a
ggsave(p2a, file='lip_amt.pdf',width=8, height=4)

liplm<-lm(value~ treatment, data=lipalt)
summary(liplm)
anova(liplm)

tukeyl <- glht(liplm, linfct = mcp(treatment = "Tukey"))
summary(tukeyl)
plot(tukeyl)
```


```{r}
dat<-read.table("../ProcessedData/all_prot_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

protalt<-data.frame('value'=c(dat[,'dr_prot'],dat[,'c_prot'],dat[,'hs_prot']),'treatment'=rep(c('dr','c', 'hs'),each=nrow(dat)), 'RIL'=rep(c(dat[,'RIL'])))

protalt<- protalt%>% mutate(treatment=fct_inorder(protalt$treatment, ordered=NA))

p3a<-ggplot(data=protalt, aes(x = treatment, y=value, color=as.factor(RIL))) +
  geom_point()+
  geom_line(aes(group = paste(as.factor(RIL)), alpha = 0.2))+
  theme(legend.position="none")+
  ylab("amount (mg/fly)")+
  stat_summary(fun.y = mean, geom = "point", size = 3, color = "black")

p3a
ggsave(p3a, file='prot_amt.pdf',width=8, height=4)

protlm<-lm(value~ treatment, data=protalt)
summary(protlm)
anova(protlm)
tukeyp <- glht(protlm, linfct = mcp(treatment = "Tukey"))
summary(tukeyp)
plot(tukeyp)

```


```{r}
dat<-read.table("../ProcessedData/all_gly_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

glyalt<-data.frame('value'=c(dat[,'dr_gly'],dat[,'c_gly'],dat[,'hs_gly']),'treatment'=rep(c('dr','c', 'hs'),each=nrow(dat)), 'RIL'=rep(c(dat[,'RIL'])))

glyalt<- glyalt%>% mutate(treatment=fct_inorder(glyalt$treatment, ordered=NA))

p4a<-ggplot(data=glyalt, aes(x = treatment, y=value, color=as.factor(RIL))) +
  geom_point()+
  geom_line(aes(group = paste(as.factor(RIL)), alpha = 0.2))+
  theme(legend.position="none")+
  ylab("amount (mg/fly)")+
  stat_summary(fun.y = mean, geom = "point", size = 3, color = "black")

p4a
ggsave(p4a, file='gly_amt.pdf',width=8, height=4)

glylm<-lm(value~ treatment, data=glyalt)
summary(glylm)
anova(glylm)

tukeyg<- glht(glylm, linfct = mcp(treatment = "Tukey"))
summary(tukeyg)
plot(tukeyg)
```

write.table(Control, "Control_tot_acq.txt", sep="\t")
write.table(DietRes, "DR_tot_acq.txt", sep="\t")
write.table(HighSugar, "HS_tot_acq.txt", sep="\t")
