---
title: "qtlMapping"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(cowplot)
library(ggplot2)
library(zoom)

load(file="../ProcessedData/btw.dat.rda")
load(file="../ProcessedData/within.dat.rda")
#load(file="../ProcessedData/p_crt.dat.rda")#protien corrected data
#load(file="../ProcessedData/pc_totacq.dat.rda")#prot corrected dta
cbPalette <- c("gray34", "#E69F00", "#009E73") #c, dr, hs
cbPalette2 <- c("blue", "red", "#000000") #comparisons 
cbPalette3<- c("seashell3","coral2", "cyan") #PCA
```

#find peaks
```{r}

max(within.dat$LOD, na.rm = TRUE) #6.5373
max(btw.dat$LOD, na.rm = TRUE) #6.953661


#subset any values above 6.5
within_peaks<-subset(within.dat, LOD>="6.5")#one peak

#Filter for specific pea to find CI is made up of 2LOD drop
within_peaks_CI<-within.dat %>% 
  select(Position, LOD, Component, Diet) %>%
  filter(LOD >= "4.5" & Component=="gly" & Diet =="hs")
#slice out 100 between position 221.5385, row 68065
find_CI<-slice(within.dat, 67965:68165)


#subset any values above 6.5 in between
btwn_peaks<-subset(btw.dat, LOD>="6.5")# 2 peaks (4 values, but positions are next to each other)
#Filter for specific pea to find CI is made up of 2LOD drop
btwn_peaks_CI_carb_c_hs<-btw.dat %>% 
  select(Position, LOD, Component, Diet) %>%
  filter(LOD >= "4.9" & Component=="carb" & Diet =="c_hs")
find_CI_bw_CARB<-slice(within.dat, 12983 :13073)

btwn_peaks_CI_prot_c_hs<-btw.dat %>% 
  select(Position, LOD, Component, Diet) %>%
  filter(LOD >= "4.64" & Component=="prot" & Diet =="c_hs")
find_CI_bw_PROT<-slice(btw.dat, 122860:122960)

```


#test if zoom works on jpegs
#if want to zoo in on specific region, plot specific area??
#for peak : which max or subset diet or compoent

Libby's comment: Do you see evidence for shared QTL for any components?

Visually, yes. Esp in Gly (2L) and Prot (x chr). AND Carb(x chr) for Between Diets plots

Note: Discuss w Libby
-How would I confirm that statistically?
-How would i search or zoom in in R for confirmation?
-Would i need to have other plots to show this?
-Would I need a table?
```{r carb}
top <-max(within.dat$LOD)
line.ww <-1
sub.dat <- within.dat[within.dat$Component=='carb',]

#for colors<- control, dr, hs
g1 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.60)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108 0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
  scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+
  labs(title="CARBOHYDRATE")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3)) +
  geom_hline(yintercept = 10, color='blue')  +
    geom_hline(yintercept = 10, color='blue') + 
  geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 5.5, label = "        LOD=6.5")

g1
ggsave(g1, file='../Plots/carb_QTL_wLabel.png')

```

##lip
```{r pressure, echo=FALSE}
top <-max(within.dat$LOD)
line.ww <-1
sub.dat <- within.dat[within.dat$Component=='lip',]

g2 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.6)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
   scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+
  labs(title="LIPID")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))+ 
    geom_hline(yintercept = 10, color='blue')  + 
    geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 5.5, label = "        LOD=6.5")

g2

ggsave(g2, file='../Plots/lip_QTL_wLabel.png')
#ggsave(g2, file='../ProcessedData/ScanResults/lip_test_withLabel.png')

```


```{r}
top <-max(within.dat$LOD)
line.ww <-1
sub.dat <- within.dat[within.dat$Component=='gly',]

g3 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.6)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
   scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+
  labs(title="GLYCOGEN")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))+ 
    geom_hline(yintercept = 10, color='blue')  + 
    geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 5.5, label = "        LOD=6.5")

#g3

#ggsave(g3, file='../ProcessedData/ScanResults/gly_test.pdf',width=8, height=4)
ggsave(g3, file='../Plots/gly_QTL_wLabel.png')

```
+ 
    geom_hline(yintercept = 10, color='blue')  + 
    annotate("text", min(sub.dat$Position), 9, label = "      LOD=10")


#test if zoom works on jpegs
#if want to zoo in on specific region, plot specific area??
#for peak : which max or subset diet or compoent

Libby's comment: Do you see evidence for shared QTL for any components?

Visually, yes. Esp in Gly (2L) and Prot (x chr). AND Carb(x chr) for Between Diets plots

Note: Discuss w Libby
-How would I confirm that statistically?
-How would i search or zoom in in R for confirmation?
-Would i need to have other plots to show this?
-Would I need a table?
```{r}
top <-max(within.dat$LOD)
line.ww <-1
sub.dat <- within.dat[within.dat$Component=='prot',]

g4 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.6)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+
  labs(title="PROTEIN")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))+ 
    geom_hline(yintercept = 10, color='blue')  + 
    geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 5.5, label = "        LOD=6.5")

g4

#ggsave(g4, file='../ProcessedData/ScanResults/prot_test.pdf',path = NULL,width=8, height=4)
ggsave(g4, file='../Plots/prot_QTL_wLabel.png')

#all_carb[which.max(all_carb$c_carb),]
```


```{r}
#combined_QTL<-plot_grid(g1, g2, g3, g4)
#ggsave(combined_QTL, file='../Plots/combined_QTL.pdf',width=8, height=4)
#ggsave(combined_QTL, file='../Plots/combined_QTL.png')

```


```{r carb}
top <-max(btw.dat$LOD)
line.ww <-1
sub.dat <- btw.dat[btw.dat$Component=='carb',]
#cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

g5<- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.6)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
  scale_colour_manual(values=cbPalette2) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ 
  labs(title="CARBOHYDRATE")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))+ 
    geom_hline(yintercept = 10, color='blue')  + 
    geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 7.5, label = "        LOD=6.5")

#ggsave(g5, file='../ProcessedData/ScanResults/carbpair_test.pdf',width=8, height=4)
ggsave(g5, file='../Plots/carb_bwQTL_wLabel.png')
```

##lip
```{r pressure, echo=FALSE}
top <-max(btw.dat$LOD)
line.ww <-1
sub.dat <- btw.dat[btw.dat$Component=='lip',]

g6 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.6)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
   scale_colour_manual(values=cbPalette2) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+
  labs(title="LIPID")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))+
  geom_hline(yintercept = 10, color='blue')  + 
    geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 5.5, label = "        LOD=6.5")


#ggsave(g6, file='../ProcessedData/ScanResults/lippair_test.pdf',width=8, height=4)
ggsave(g6, file='../Plots/lip_bwQTL_wLabel.png')

```


```{r}
top <-max(btw.dat$LOD)
line.ww <-1
sub.dat <- btw.dat[btw.dat$Component=='gly',]

g7 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.6)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
   scale_colour_manual(values=cbPalette2) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ 
  labs(title="GLYCOGEN")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))+
  geom_hline(yintercept = 10, color='blue')  + 
    geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 5.5, label = "        LOD=6.5")

#ggsave(g7, file='../ProcessedData/ScanResults/glypair_test.pdf',width=8, height=4)
ggsave(g7, file='../Plots/gly_bwQTL_wLabel.png')

```


```{r}
top <-max(btw.dat$LOD)
line.ww <-1
sub.dat <- btw.dat[btw.dat$Component=='prot',]

g8 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.6)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette2) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+
  labs(title="PROTIEN")+
  expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))+
  geom_hline(yintercept = 10, color='blue')  + 
    geom_hline(yintercept= 6.5, color= 'red')+
    annotate("text", min(sub.dat$Position), 9, label = "        LOD=10")+
    annotate("text", min(sub.dat$Position), 5.5, label = "        LOD=6.5")


#ggsave(g8, file='../ProcessedData/ScanResults/protpair_test.pdf',path = NULL,width=8, height=4)
ggsave(g8, file='../Plots/prot_bwQTL_wLabel.png')

```


```{r}
#combined_QTL_bwDIET<-plot_grid(g5, g6, g7, g8)
#ggsave(combined_QTL_bwDIET, file='../Plots/combined_QTL_bwDIET.pdf',width=8, height=4)
#ggsave(combined_QTL_bwDIET, file='../Plots/combined_QTL_bwDIET.png')

```


##Protien correction
#change colors of diet.
```{r}
top <-max(p_crt.dat$LOD)
line.ww <-1
sub.dat <- p_crt.dat[p_crt.dat$Component=='carb',]

g9 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.65)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))


#ggsave(g9, file='../ProcessedData/ScanResults/carb_p_crt_test.pdf',path = NULL,width=8, height=4)
#ggsave(g9, file='../ProcessedData/ScanResults/carb_p_crt_test.png')

```

#run from here on out
```{r}
top <-max(p_crt.dat$LOD)
line.ww <-1
sub.dat <- p_crt.dat[p_crt.dat$Component=='gly',]

g10 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.65)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))


#ggsave(g10, file='../ProcessedData/ScanResults/gly_p_crt_test.pdf',path = NULL,width=8, height=4)
#ggsave(g10, file='../ProcessedData/ScanResults/gly_p_crt_test.png')

```

```{r}
top <-max(p_crt.dat$LOD)
line.ww <-1
sub.dat <- p_crt.dat[p_crt.dat$Component=='lip',]

g11 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.65)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))

#g11

#ggsave(g11, file='../ProcessedData/ScanResults/lip_p_crt_test.pdf',path = NULL,width=8, height=4)
#ggsave(g11, file='../ProcessedData/ScanResults/lip_p_crt_test.png')

```

```{r}
top <-max(p_crt.dat$LOD)
line.ww <-1
sub.dat <- p_crt.dat[p_crt.dat$Component=='prot',]

g12 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.65)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))

#g12

#ggsave(g12, file='../ProcessedData/ScanResults/prot_fromp_crt_test.pdf',path = NULL,width=8, height=4)
#ggsave(g12, file='../ProcessedData/ScanResults/prot_fromp_crt_test.png')
```

```{r}
top <-max(pc_totacq.dat$LOD)
line.ww <-1
sub.dat <- pc_totacq.dat[pc_totacq.dat$Component=='PC1',]

g13 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.65)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))

g13

#ggsave(g13, file='../ProcessedData/ScanResults/PC1_test.pdf',path = NULL,width=8, height=4)
ggsave(g13, file='../ProcessedData/ScanResults/PC1_test.png')
```

```{r}
top <-max(pc_totacq.dat$LOD)
line.ww <-1
sub.dat <- pc_totacq.dat[pc_totacq.dat$Component=='PC2',]

g14 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.65)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))

g14

#ggsave(g14, file='../ProcessedData/ScanResults/PC2_test.pdf',path = NULL,width=8, height=4)
ggsave(g14, file='../ProcessedData/ScanResults/PC2_test.png')

```

```{r}
top <-max(pc_totacq.dat$LOD)
line.ww <-1
sub.dat <- pc_totacq.dat[pc_totacq.dat$Component=='tot_acq',]

g15 <- ggplot(sub.dat, aes(x=Position, y=LOD,color=Diet))+
  geom_rect(xmin=66.3,ymin=-10,xmax=120.3,ymax=top+10,fill='grey80',color='grey80')+
  geom_rect(xmin=174,ymin=-10,xmax=221,ymax=top+10,fill='grey80',color='grey80')+
  geom_line(size=line.ww,alpha=0.65)+
  scale_x_continuous(breaks=c(0,66.3,120,174,221,277,33.15,98.3,145,205,249), 
                     labels=c(0,"66  0",54,"108  0",47,103,'\nX','\n2L','\n2R','\n3L','\n3R'))+
 scale_colour_manual(values=cbPalette) +
  theme(axis.ticks.x=element_blank())+
  ylab("LOD")+
  xlab("Position (cM)")+ expand_limits(y=c(0,11))+ scale_y_continuous(breaks=seq(0,11,3))

g15

#ggsave(g15, file='../ProcessedData/ScanResults/totacq_test.pdf',path = NULL,width=8, height=4)
ggsave(g15, file='../ProcessedData/ScanResults/totacq_test.png')

```
