---
title: "ProtienVsMass"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(cowplot)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(plyr)
setwd("C:/Users/Anna/Dropbox/AMP_EGK/Projects/Ch1_RILs/Scripts")
```

```{r cars}
all_molec<-read.table("../ProcessedData/all_flies_proccessed_checked.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

all_molec$RIL<-gsub("[^[:digit:]]", "", all_molec$Line)#Make RIL column
all_molec$Treat<-gsub("[[:digit:]]","",all_molec$Line)#Make Treatment column
whole.dat<-all_molec[complete.cases(all_molec), ] #columns w NA removed. 

```
all_molec_w_plates<-read.table("../ProcessedData/all_molec_w_plate.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE) #this has also removed anything that has NA's in it. Includes all other misc info.

all_molec<-select(all_molec_w_plates, Line, PLATE, RIL, Treat, c_perfly.y, g_perfly.y, p_perfly.y, lperfly.y)

all_molec<-rename(all_molec_w_plt, c("c_perfly.y"="c_perfly", "g_perfly.y"="g_perfly", "p_perfly.y"="p_perfly", "lperfly.y"="lperfly"))


whole.dat<-all_molec[complete.cases(all_molec), ] #columns w NA removed. 

```{r}
which(all_molec$c_perfly<.01)
which(all_molec$c_perfly>.01 & all_molec$c_perfly<.1)
which(all_molec$c_perfly<.1)
```


```{r}
a <- prcomp(~ c_perfly + lperfly +p_perfly, data = whole.dat, center = TRUE, scale. = TRUE)
summary(a)
print(a)

b <- prcomp(~ c_perfly + lperfly +p_perfly+ g_perfly, data = whole.dat, center = TRUE, scale. = TRUE)
summary(b)
print(b)

PCBi<-data.frame(b$x,Treatment=whole.dat$Treat)


ggplot(PCBi,aes(x=PC1,y=PC2,col=Treatment))+
   geom_point(size=1,alpha=0.5)+ 
   theme_classic()

#ggplot(PCBj,aes(x=PC1,y=PC2,col=Plate))+
   geom_point(size=1,alpha=0.5)+ 
   theme_classic()

v <- prcomp(~ c_perfly + lperfly, data = whole.dat, center = TRUE, scale. = TRUE)
summary(v)
print(v)

w <- prcomp(~ c_perfly + g_perfly, data = whole.dat, center = TRUE, scale. = TRUE)
summary(w)
print(w)
```


```{r}
C_diet<-subset(all_molec, Treat=="C")
DR_diet<-subset(all_molec, Treat=="DR")
HS_diet<-subset(all_molec, Treat=="HS")


control_pca <- prcomp(~ c_perfly + lperfly +p_perfly+ g_perfly, data = C_diet, center = TRUE, scale. = TRUE)
summary(control_pca)
print(control_pca)

biplot(control_pca)
PCB_control<-data.frame(control_pca$x,Treatment=whole.dat$Treat)

#Control diet PCA

PC_control <- data.frame(pc1 = control_pca$x[, 1],
                 pc2 = control_pca$x[, 2],
                 pc3 = control_pca$x[, 3],
                 pc4 = control_pca$x[, 4])
PC_control

pc_control_plot <- ggplot(PC_control, aes(pc1, pc2, pc3, pc4)) +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_hline(yintercept = 0, color = "red", size = 1.5) +
  geom_point() +
  coord_fixed()
print(pc_control_plot)

```

```{r}
dr_pca <- prcomp(~ c_perfly + lperfly +p_perfly+ g_perfly, data = DR_diet, center = TRUE, scale. = TRUE)
summary(dr_pca)
print(dr_pca)
```

##High Sugar PCA
```{r}
hs_pca <- prcomp(~ c_perfly + lperfly +p_perfly+ g_perfly, data = HS_diet, center = TRUE, scale. = TRUE)
summary(hs_pca)
print(hs_pca)
```


ctl_pca_a<- prcomp(~ c_perfly + lperfly +p_perfly, data = C_diet, center = TRUE, scale. = TRUE)
summary(ctl_pca_a)
print(ctl_pca_a)

dr_pca_a<- prcomp(~ c_perfly + lperfly +p_perfly, data = DR_diet, center = TRUE, scale. = TRUE)
summary(dr_pca_a)
print(dr_pca_a)

hs_pca_a<- prcomp(~ c_perfly + lperfly +p_perfly, data = HS_diet, center = TRUE, scale. = TRUE)
summary(hs_pca_a)
print(hs_pca_a)
##Dietary Restriction PCA


#also make biplots

##find the correlations value
pairs(all_carb[, -1], gap=0,pch=".")
carb_pfly<-all_molec$c_perfly
prot_pfly<-all_molec$p_perfly
cor(carb_pfly,prot_pfly)
cor(prot_pfly,carb_pfly)

```{r pressure, echo=FALSE}

c_g<-ggplot(all_molec, aes(c_perfly, g_perfly )) + geom_point()
cor.test(x=all_molec$c_perfly, y=all_molec$g_perfly, method = "pearson")
c_g<-(c_g + ggtitle("overall: glycogen by carboydrate"))
c_g<-ggscatter(all_molec, x = "c_perfly", y = "g_perfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson") #.014
#ggsave(c_g, file='../ProcessedData/CorrelationPlots/overall_c_g.png')


c_p<-ggplot(all_molec, aes(c_perfly, p_perfly )) + geom_point()
cor.test(all_molec$c_perfly, all_molec$p_perfly,  method = "pearson")
c_p<-(c_p + ggtitle("overall: protein by carboydrate"))
c_p<-ggscatter(all_molec, x = "c_perfly", y = "p_perfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson") #.1987
#ggsave(c_p, file='../ProcessedData/CorrelationPlots/overall_c_p.png')

c_l<-ggplot(all_molec, aes(c_perfly, lperfly )) + geom_point()
c_l<-(c_l + ggtitle("overall: lipid by carboydrate"))
cor.test(all_molec$c_perfly, all_molec$lperfly,  method = "pearson")
c_l<-ggscatter(all_molec, x = "c_perfly", y = "lperfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson")#.3553
##ggsave(c_l, file='../ProcessedData/CorrelationPlots/overall_c_l.png')

g_p<-ggplot(all_molec, aes(g_perfly, p_perfly )) + geom_point()
g_p<-(g_p + ggtitle("overall: glycogen by protien"))
cor.test(all_molec$g_perfly, all_molec$p_perfly,  method = "pearson")
g_p<-ggscatter(all_molec, x = "g_perfly", y = "p_perfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson") #-.0498
#ggsave(g_p, file='../ProcessedData/CorrelationPlots/overall_g_p.png')


g_l<-ggplot(all_molec, aes(g_perfly, lperfly )) + geom_point()
g_l<-(g_l + ggtitle("overall: glycogen by lipid"))
#ggsave(g_l, file='../ProcessedData/CorrelationPlots/overall_g_l.png')
cor.test(all_molec$g_perfly, all_molec$lperfly,  method = "pearson")#-.08
g_l<-ggscatter(all_molec, x = "g_perfly", y = "lperfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson")


g_c<-ggplot(all_molec, aes(g_perfly, c_perfly )) + geom_point()
g_c<-(g_c + ggtitle("overall: glycogen by carbohydrate"))
#ggsave(g_c, file='../ProcessedData/CorrelationPlots/overall_g_c.png')
cor.test(all_molec$g_perfly, all_molec$c_perfly,  method = "pearson") #.014
g_c<-ggscatter(all_molec, x = "g_perfly", y = "c_perfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson")

l_g<-ggplot(all_molec, aes(lperfly, g_perfly )) + geom_point()
l_g<-(l_g + ggtitle("overall: lipid by glycogen"))
#ggsave(l_g, file='../ProcessedData/CorrelationPlots/overall_l_g.png')
cor.test(all_molec$lperfly, all_molec$g_perfly,  method = "pearson") #-.0842
l_g<-ggscatter(all_molec, x = "lperfly", y = "g_perfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson")


l_p<-ggplot(all_molec, aes(lperfly, p_perfly )) + geom_point()
l_p<-(l_p + ggtitle("overall: lipid by protien"))
#ggsave(l_p, file='../ProcessedData/CorrelationPlots/overall_l_p.png')
cor.test(all_molec$lperfly, all_molec$p_perfly,  method = "pearson")#.339
l_p<-ggscatter(all_molec, x = "lperfly", y = "p_perfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson")
#

l_c<-ggplot(all_molec, aes(lperfly, c_perfly )) + geom_point()
l_c<-(l_c + ggtitle("overall: lipid by carbohydrate"))
#ggsave(l_c, file='../ProcessedData/CorrelationPlots/overall_l_c.png')
cor.test(all_molec$lperfly, all_molec$c_perfly,  method = "pearson") #.3553
l_c<-ggscatter(all_molec, x = "lperfly", y = "c_perfly", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson")
```

```{r}
plot_grid(c_g, c_p, c_l, g_c, g_p, g_l, l_c, l_p, l_g)
```


#treatment
```{r}

AvgTab<-read.table("../ProcessedData/all_flies_proccessed_checked.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

first<-AvgTab[1:6,]

AvgTab$RIL<-gsub("[^[:digit:]]", "", AvgTab$Line)#Make RIL column
AvgTab$Treat<-gsub("[[:digit:]]","",AvgTab$Line)#Make Treatment column

C_diet<-subset(AvgTab, Treat=="C")
DR_diet<-subset(AvgTab, Treat=="DR")
HS_diet<-subset(AvgTab, Treat=="HS")

ggplot(C_diet, aes(c_perfly, g_perfly )) + geom_point()
ggplot(C_diet, aes(c_perfly, p_perfly )) + geom_point()
ggplot(C_diet, aes(c_perfly, lperfly )) + geom_point()

ggplot(DR_diet, aes(c_perfly, g_perfly )) + geom_point()
ggplot(DR_diet, aes(c_perfly, p_perfly )) + geom_point()
ggplot(DR_diet, aes(c_perfly, lperfly )) + geom_point()

ggplot(HS_diet, aes(c_perfly, g_perfly )) + geom_point()
ggplot(HS_diet, aes(c_perfly, p_perfly )) + geom_point()
ggplot(HS_diet, aes(c_perfly, lperfly )) + geom_point()
```

The Pearson product-moment correlation coefficient (or Pearson correlation coefficient, for short) is a measure of the strength of a linear association between two variables and is denoted by r. Basically, a Pearson product-moment correlation attempts to draw a line of best fit through the data of two variables, and the Pearson correlation coefficient, r, indicates how far away all these data points are to this line of best fit (i.e., how well the data points fit this new model/line of best fit).
https://statistics.laerd.com/statistical-guides/pearson-correlation-coefficient-statistical-guide.php

Strength 
of Association	Positive	Negative
Small	          .1 to .3	-0.1 to -0.3
Medium	        .3 to .5	-0.3 to -0.5
Large	          .5 to 1.0	-0.5 to -1.0

```{r}
ggplot(C_diet, aes(lperfly, c_perfly)) + geom_point()
cor.test(C_diet$lperfly, C_diet$c_perfly,  method = "pearson") #.2778

ggplot(DR_diet, aes(lperfly, c_perfly)) + geom_point()
cor.test(DR_diet$lperfly, DR_diet$c_perfly,  method = "pearson") #.47

ggplot(HS_diet, aes(lperfly, c_perfly )) + geom_point()
cor.test(HS_diet$lperfly, HS_diet$c_perfly,  method = "pearson") # .311 not ...=#.131


ctrl_l_p<-ggplot(C_diet, aes(lperfly,p_perfly )) + geom_point()
cor.test(C_diet$lperfly, C_diet$p_perfly,  method = "pearson") #.393
ctrl_l_p<-(ctrl_l_p + ggtitle("control diet: lipid by protein"))
ctrl_l_p
ggsave(ctrl_l_p, file='../ProcessedData/CorrelationPlots/ctl_l_p.png')

dr_l_p<-ggplot(DR_diet, aes(p_perfly, lperfly )) + geom_point()
cor.test(DR_diet$lperfly, DR_diet$p_perfly,  method = "pearson")#.326
dr_l_p<-(dr_l_p + ggtitle("dietary restriction: lipid by protein"))
ggsave(dr_l_p, file='../ProcessedData/CorrelationPlots/dr_l_p.png')

hs_l_p<-ggplot(HS_diet, aes(p_perfly, lperfly )) + geom_point()
cor.test(HS_diet$lperfly, HS_diet$p_perfly,  method = "pearson") #.305
hs_l_p<-(hs_l_p + ggtitle("high sugar: lipid by protein"))
ggsave(hs_l_p, file='../ProcessedData/CorrelationPlots/hs_l_p.png')

```




??Delete this??
```{r}
#read in table
setwd("C:/Users/Anna/Dropbox/AMP_EGK/Projects/Ch1_RILs/Scripts")

dat<-read.table("../RawData/Combined/massteset.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)

c_std<-read.table("../RawData/StdCurves/carbstdcurvev4.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
g_std<-read.table("../RawData/StdCurves/glystdcurvev4.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
p_std<-read.table("../RawData/StdCurves/protienstdcurvev5.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
l525_std<-read.table("../RawData/StdCurves/lipid525stdcurvev6.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)

#avgstdc<-read.table("../RawData/StdCurves/c_standardcurve",sep="\t",header=TRUE,stringsAsFactors=FALSE)
#avgstdg<-read.table("../RawData/StdCurves/g_standardcurve",sep="\t",header=TRUE,stringsAsFactors=FALSE)
avgstdl525<-read.table("../RawData/StdCurves/l525_standardcurve",sep="\t",header=TRUE,stringsAsFactors=FALSE)
#avgstdp<-read.table("../RawData/StdCurves/p_standardcurve",sep="\t",header=TRUE,stringsAsFactors=FALSE)


#add treatmet and RIL column
dat$RIL<-as.numeric(gsub("[^[:digit:]]", "", dat$Line))#Make RIL column
dat$Treat<-gsub("[[:digit:]]","",dat$Line)#Make Treatment column

which(dat$RIL>2000)
#loop for carbohydrates
carbohydrates<-data.frame("amount"=numeric(length=0), "line"=numeric(length=0), "diet"=character(length=0), "plate"=character(length=0), "flies"=character(length=0), stringsAsFactors=FALSE)

for (plateid in unique(dat$PLATE))
{
  std.c<-subset(c_std, PLATE== plateid)
  star<-lm(abs~amount, data=c_std)
  plate.s<-subset(dat,PLATE== plateid)
  workwork<-(plate.s$CARB625-star$coefficients[1])/star$coefficients[2]
  carbohydrates.s<-data.frame("amount"=workwork, "line"=plate.s$RIL, "diet"=plate.s$Treat, "plate"=plate.s$PLATE, "flies"=plate.s$FLIES, stringsAsFactors=FALSE)
  carbohydrates<-rbind(carbohydrates, carbohydrates.s)
}
#calculate amount per fly.
dat$c_perfly<-(carbohydrates$amount*(150/1400))/(carbohydrates$flies)

#GLYCOGEN
glycogen<-data.frame("amount"=numeric(length=0), "line"=numeric(length=0), "diet"=character(length=0), "plate"=character(length=0), "flies"=character(length=0), stringsAsFactors=FALSE)

for (plateid in unique(dat$PLATE))
{
  std.g<-subset(g_std, PLATE== plateid)
  star<-lm(abs~amount, data=c_std)
  plate.s<-subset(dat,PLATE== plateid)
  workwork<-(plate.s$GLY625-star$coefficients[1])/star$coefficients[2]
  glycogen.s<-data.frame("amount"=workwork, "line"=plate.s$RIL, "diet"=plate.s$Treat, "plate"=plate.s$PLATE, "flies"=plate.s$FLIES, stringsAsFactors=FALSE)
  glycogen<-rbind(glycogen, glycogen.s)
}

#calculate amount per fly.
dat$g_perfly<-(glycogen$amount*(150/1000))/(glycogen$flies)

###loop for lipids
lipids525<-data.frame("amount"=numeric(length=0), "line"=numeric(length=0), "diet"=character(length=0), "plate"=character(length=0), "flies"=character(length=0), stringsAsFactors=FALSE)

for (plateid in unique(dat$PLATE))
{
  #std.p<-subset(p_std, PLATE== plateid)
  std.l525<-avgstdl525
  star<-lm(abs~amount, data=l525_std)
  plate.s<-subset(dat,PLATE== plateid)
  workwork<-(plate.s$LIP525-star$coefficients[1])/star$coefficients[2]
  lipids525.s<-data.frame("amount"=workwork, "line"=plate.s$RIL, "diet"=plate.s$Treat, "plate"=plate.s$PLATE, "flies"=plate.s$FLIES, stringsAsFactors=FALSE)
  lipids525<-rbind(lipids525, lipids525.s)
}

#calculate amount per fly.
dat$lperfly<-(lipids525$amount*(100/1400))/(lipids525$flies)


###loop for protiens
protiens<-data.frame("amount"=numeric(length=0), "line"=numeric(length=0), "diet"=character(length=0), "plate"=character(length=0), "flies"=character(length=0), stringsAsFactors=FALSE)

for (plateid in unique(dat$PLATE))
{
  std.p<-subset(p_std, PLATE== plateid)
  star<-lm(abs~amount, data=p_std)
  plate.s<-subset(dat,PLATE== plateid)
  workwork<-(plate.s$PROT595-star$coefficients[1])/star$coefficients[2]
  protiens.s<-data.frame("amount"=workwork, "line"=plate.s$RIL, "diet"=plate.s$Treat, "plate"=plate.s$PLATE, "flies"=plate.s$FLIES, stringsAsFactors=FALSE)
  protiens<-rbind(protiens, protiens.s)
}

###calculate protien amount per fly.
dat$p_perfly<-(protiens$amount*(2/180))/(protiens$flies)

which(dat$RIL>2000)
dat$RIL[which(dat$RIL>2000)]<-dat$RIL[which(dat$RIL>2000)]-22000
##remove the 22000 from 'Line' here
#which(data$Line>2000)

write.table(dat, "masstesting.txt", sep="\t")

```

test<-cbind(masstest[,14],masstest[,14],masstest[,18])
ggplot(masstest, aes(PROTCONC, MASS)) + geom_point()
mass_perfly<-masstest[,14],masstest[,18]


THIS IS WHERE THE MASSES START!!!

```{r}
masstest<-read.table("Processed_perflyconc_wMass.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
masstest$m_perfly<- masstest$MASS/masstest$FLIES

mass_pfly1<-ggplot(masstest, aes(p_perfly, m_perfly )) + geom_point()
mass_pfly2<-ggplot(masstest, aes(m_perfly, p_perfly )) + geom_point()

which(masstest$p_perfly >.005) #2 values
masstest$p_perfly[masstest$p_perfly >.005] <- NA
masstest$m_perfly[masstest$m_perfly >.005] <- NA

mass_pfly1<-ggplot(masstest, aes(p_perfly, m_perfly )) + geom_point()
mass_pfly2<-ggplot(masstest, aes(m_perfly, p_perfly )) + geom_point()

mass_pfly1
mass_pfly2
```


